
\vspace{\baselineskip}
\vspace{\baselineskip}
\begin{multicols}{2}
\textbf{Authors $\&$  Contributors}\par


\vspace{\baselineskip}

\end{multicols}
\begin{itemize}
	\item Prof. Dr.-Ing. Boris Otto, Fraunhofer ISST 

	\item Sebastian Steinbuß, International Data Spaces Association 

	\item Andreas Teuscher, SICK 

	\item Dr.-Ing. Steffen Lohmann, Fraunhofer IAIS 
\end{itemize}

\vspace{\baselineskip}
\begin{multicols}{2}
\begin{itemize}
	\item Prof. Dr. Sören Auer, L3S Research Center
	\item Sebastian Bader, Fraunhofer IAIS
	\item Harrie Bastiaansen, TNO
	\item Hannes Bauer, orbiter
	\item Pascal Birnstil, Fraunhofer IOSB
	\item Martin Böhmer, Fraunhofer IML
	\item 	Dr. Jürgen Bohn, Schaeffler
	\item 	Gernot Böge, FIWARE Foundation
	\item 	Gerd Brost, Fraunhofer AISEC
	\item 	Juan Ceballos, Deutsche Telekom
	\item 	Dr.-Ing. Jan Cirullies, Fraunhofer ISST
	\item 	Constantin Ciureanu, T-Systems
	\item 	Eva Corsi, Boehringer Ingelheim
	\item 	Simon Dalmolen, TNO
	\item 	Søren Danielsen, GateHouse Logistics
	\item 	AlexanderDuisberg, Bird \& Bird
	\item 	Andreas Eitel, Fraunhofer IESE
	\item 	Thilo Ernst, Fraunhofer FOKUS
	\item 	Fabiana Fournier, IBM
	\item 	Marquart Franz, Siemens AG
	\item 	Dr. Sandra Geisler, Fraunhofer FIT
	\item 	Joshua Gelhaar, Fraunhofer ISST
	\item 	Roland Gude, Fraunhofer IAIS
	\item 	Dr.-Ing. Christian Haas, Fraunhofer IOSB
	\item 	Jürgen Heiles, Siemens
	\item 	 Burkhard Heisen, cybus
	\item 	Juanjo Hierro, FIWARE
	\item 	Joachim Hoernle, ATOS
	\item 	Manuel Huber, Fraunhofer AISEC
	\item 	Christian Jung, Fraunhofer IESE
	\item 	Prof. Dr. Jan Jürjens, Fraunhofer ISST
	\item 	Dr. Anna Kasprzik, L3S Research Center
	\item 	Dr. Markus Ketterl, msg systems
	\item 	Judith Koetzsch, Rittal
	\item 	Jacob Köhler, Deloitte
	\item 	Dr. Christoph Lange, Fraunhofer IAIS
	\item 	Dorothea Langer, Deloitte
	\item 	Jörg Langkau, nicos
	\item 	Dominik Lis, Fraunhofer ISST
	\item 	Sven Löffler, T-Systems
	\item 	Dr. Ulrich Löwen, Siemens
	\item 	Dr. Christian Mader, Fraunhofer IAIS
	\item 	Bernhard Müller, SICK
	\item 	Nadja Menz, Fraunhofer FOKUS
	\item 	Christoph Mertens, International Data Spaces Association
	\item 	Andreas Müller, Schaeffler
	\item 	Lars Nagel, International Data Spaces Association
	\item 	Dr. Ralf Nagel, Fraunhofer ISST
	\item 	Harri Nieminen, Fastems
	\item 	Thomas Reitelbach, Bosch
	\item 	Aleksei Resetko, PricewaterhouseCoopers
	\item 	Daniel Pakkala, VTT Technical Research Centre of Finland
	\item 	Florian Patzer, Fraunhofer IOSB
	\item 	Heinrich Pettenpohl, Fraunhofer ISST
	\item 	René Pietzsch, eccenca
	\item 	Jaroslav Pullmann, Fraunhofer FIT
	\item 	Matthijs Punter, TNO
	\item 	Dr. Christoph Quix, Fraunhofer FIT
	\item 	Aleksei Resetko, PwC
	\item 	Dr. Dominik Rohrmus, Siemens
	\item 	Lena Romer, Boehringer Ingelheim
	\item 	Jörg Sandlöhken, REWE Systems
	\item 	Patrick Schöwe, agma data
	\item 	Daniel Schulz, Fraunhofer IAIS
	\item 	Dr. Julian Schütte, Fraunhofer AISEC
	\item 	Dr. Karsten Schweichhart, Deutsche Telekom
	\item 	Inna Skarbowski, IBM
	\item 	Prof. Egbert-Jan Sol, TNO
	\item 	Peter Sorowka, Cybus
	\item 	Prof. Dr.-Ing. Gernot Spiegelberg, Siemens
	\item 	Markus Spiekermann, Fraunhofer ISST
	\item 	Christian Spohn, ATOS
	\item 	Gerrit Stöhr, GESIS
	\item 	Erwin Tanger, ATOS
	\item 	Dr. Michael Theß, Signal Cruncher
	\item 	Dr. Sebastian Tramp, eccenca
	\item 	Dr. Mona Wappler, thyssenkrupp
	\item 	Ann-Christin Weiergräber, Uniklinik RWTH Aachen
	\item 	Dr. Sven Wenzel, Fraunhofer ISST
	\item 	Oliver Wolff, Advaneo
	\item 	Heike Wörner, DB Schenker


\vspace{\baselineskip}

\end{itemize}
\end{multicols}
